High-Dimensional Regularized Discriminant Analysis

### 2016-01-31 reports/paper-hdrda.Rnw
Slight reword
Applied CSDA LaTeX template #19
Need to fix line numbers.

\documentclass{article}

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm, natbib, setspace}
\usepackage{algorithm2e, authblk, url}

@@

\pagestyle{plain}
%----------------Page dimensions ----------------
\oddsidemargin 0.0in
\evensidemargin 0.0in
\topmargin -0.75in
\leftmargin 0in
\headheight 0.0in
\headsep 0.5in
\footskip 0.5in
\footnotesep 0.0in
\textwidth 6.5in
\textheight 9.5in

@@

@@

%\author{John A. Ramey, Caleb K. Stein, Phil D. Young, and Dean M. Young}

\author[a]{John A. Ramey}
\author[b]{Caleb K. Stein}
\author[c]{Phil D. Young}
\author[d]{Dean M. Young}
\affil[a]{uStudio, Inc.}
\affil[b]{Myeloma Institute, University of Arkansas for Medical Sciences}
\affil[c]{Department of Management and Information Systems, Baylor University}
\affil[d]{Department of Statistical Science, Baylor University}

\renewcommand\Authands{ and }

\maketitle

\doublespacing

@@

@@

The remainder of this paper is organized as follows. In Section
\ref{sec:preliminaries} we present the discrimination problem and necessary
notation to describe our contributions. In Section \ref{sec:rda} we present the
\emph{HDRDA} classifier along with its interpretation, properties, and
computationally efficient model-selection procedure. In Section \ref{sec:sims}
we describe our simulation studies of artificial and real data sets and describe
the experimental results. We conclude with a brief discussion in Section
\ref{sec:discussion}.

>>>>

\documentclass[review]{elsarticle}

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm, natbib}
\usepackage{algorithm2e, url, lineno}

@@

%----------------Page dimensions ----------------
\oddsidemargin 0.0in
\evensidemargin 0.0in
\topmargin -0.75in
\leftmargin 0in
\headheight 0.0in
\headsep 0.5in
\footskip 0.5in
\footnotesep 0.0in
\textwidth 6.5in
\textheight 9.5in

@@

\begin{frontmatter}

@@

\author[jar]{John A. Ramey\cortext[cor1]{Corresponding author}}
\author[cks]{Caleb K. Stein}
\author[pdy]{Phil D. Young}
\author[dmy]{Dean M. Young}
\address[jar]{uStudio, Inc.}
\address[cks]{Myeloma Institute, University of Arkansas for Medical Sciences}
\address[pdy]{Department of Management and Information Systems, Baylor University}
\address[dmy]{Department of Statistical Science, Baylor University}

@@

\end{frontmatter}

\linenumbers

@@

The remainder of this paper is organized as follows. In Section
\ref{sec:preliminaries} we present the classification problem and necessary
notation to describe our contributions. In Section \ref{sec:rda} we present the
\emph{HDRDA} classifier along with its interpretation, properties, and
computationally efficient model-selection procedure. In Section \ref{sec:sims}
we describe our simulation studies of artificial and real data sets and describe
the experimental results. We conclude with a brief discussion in Section
\ref{sec:discussion}.
